From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-09 Pi+/paper/reversible1.tex

All of this is only half the story, however. A sound semantics for $\PiLang$ in weak rig
groupoids was established by \citet{caretteComputingSemiringsWeak2016}, and conjectured to be complete. For this
semantics, rig groupoid \emph{coherence conditions} that identify different syntactic representations of the same
permutation~\cite{laplaza72,Carette2016} were collected  in a
second level of $\PiLang$ syntax as level-2 combinators.  Each level-2 combinator is of the form $c_1 \isotwo c_2$ for appropriate
$c_1$ and $c_2$ of the same level-1 type $A \isoone B$ and asserts that $c_1$ and $c_2$ denote the same bijection. For
example, we have the following level-2 combinators dealing with associativity:

>>>>

All of this is only half the story, however. A sound semantics for $\PiLang$ in weak rig
groupoids was established by \citet{caretteComputingSemiringsWeak2016}, and conjectured to be complete. For this
semantics, rig groupoid \emph{coherence conditions} that identify different syntactic representations of the same
permutation~\cite{laplaza72,caretteComputingSemiringsWeak2016} were collected  in a
second level of $\PiLang$ syntax as level-2 combinators.  Each level-2 combinator is of the form $c_1 \isotwo c_2$ for appropriate
$c_1$ and $c_2$ of the same level-1 type $A \isoone B$ and asserts that $c_1$ and $c_2$ denote the same bijection. For
example, we have the following level-2 combinators dealing with associativity:
